---
title: "Question set II"
author: "Hunter Goehring"
date: "2023-03-06"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
choco <- read.csv("https://ds202-at-isu.github.io/labs/data/choco.csv")
head(choco)
```
```{r}
library(ggplot2)
```


Question set 2:  
1. For each of the questions below provide at least one graphic as a basis for your answer.  

  1. How are ratings distributed? Draw a histogram of ratings and describe it. Don't forget to mention outliers, if there are any.  
```{r}
ggplot(data = choco, aes(x = Rating)) + geom_histogram()
```
      
      Ratings are distributed across a scale from 1 being Unpleasant, to 5 being Elite. The majority of ratings fall between 2 (Disappointing) and 4 (Premium). There are a couple outliers that recieved scores close to 1 and an outlier near 5.
    
  2. Do ratings depend on the cocoa percentage of a chocolate bar?  
```{r}
ggplot(data = choco, aes(x = Rating, y = Cocoa.Pct)) + geom_jitter()
```
      
      The data doesn't appear to show any dependencies between ratings and the cocoa percentage. There are outliers with similar percentages that have completely opposite ratings.  
    
  3. How do ratings compare across different company locations? Focus on the three locations with the most ratings.  
```{r}
loc = dplyr::filter(choco, Company.Location %in% c("U.S.A.", "France", "Canada"))
ggplot(loc, aes(x=Company.Location, y = Rating)) + geom_boxplot()
```
    
    The average ratings from each location are all fairly similar to each other. Canada has a higher upper quartile than the other two locations, whereas U.S.A. has the lowest lower quartile. France has two low outliers that go along with the U.S.A.'s one.
  